Relevance-based Quantization of Scattering Features for Unsupervised Mining of Environmental Audio

### 2018-07-30 paper/lostanlenRelevanceScattering.tex
list DCASE classes

It is worth mentionning that this task typically falls into a unsupervised paradigm where no prior knowldge is used to model a given scene. For each scene $s$, a model is compute $M_s$ is computed. The similarity among the scene $s_1$ and $s_2$ is computed as the similarity, see Section~\ref{sec:experiments} for further details. The BoF approach is also widely used in a supervised fashion for solving a classification task~\cite{7100934}. In this case, each class of scenes of a given typology, say \{\emph{park, boulevard, square}\}, is modeled by a GMM trained on scenes taken from a training set. In order to predict the class of a given scene $s$, the likelihood each model given the scene are computed. The scene is then labeled park if the likelihood of the GMM trained on park scenes is higher than the other likelihoods.

@@

The experiments in this paper are carried out on the DCASE 2013 dataset~\cite{7100934}.
Although the dataset was constructed for the task of acoustic scene classification, where the goal is to correctly assign the class of a given recording, we can use the same recordings and class labels for the task of acoustic scene similarity retrieval.
The dataset consists of two parts, a public and a private subset, each made up of $100$ acoustic scene recordings sampled at $44100\,\mathrm{Hz}$ and $30$ seconds in duration. The dataset is evenly divided into $10$ acoustic scene classes. The recordings were made by three different recordists at a wide variety of locations in the Greater London area over a period of several months. No
systematic variations in the recordings covaried with scene
type: all recordings were made under moderate weather conditions, at varying times of day and week, and each recordist recorded each scene type. As a result, the dataset enjoys significant intra-class diversity while remaining of manageable size, making it suitable for evaluation of algorithmic design choices~\cite{lagrange:hal-01082501}.

>>>>

It is worth mentionning that this task typically falls into a unsupervised paradigm where no prior knowldge is used to model a given scene. For each scene $s$, a model is compute $M_s$ is computed. The similarity among the scene $s_1$ and $s_2$ is computed as the similarity, see Section~\ref{sec:experiments} for further details. The BoF approach is also widely used in a supervised fashion for solving a classification task~\cite{7100934}. In this case, each class of scenes from a given typology, say \{\emph{park, boulevard, square}\}, is modeled by a GMM trained on scenes taken from a training set. In order to predict the class of a given scene $s$, the likelihood each model given the scene are computed. The scene is then labeled park if the likelihood of the GMM trained on park scenes is higher than all other likelihoods.

@@

The experiments in this paper are carried out on the DCASE 2013 dataset~\cite{7100934}.
Although the dataset was constructed for the task of acoustic scene classification, where the goal is to correctly assign the class of a given recording, we can use the same recordings and class labels for the task of acoustic scene similarity retrieval.
The dataset consists of two parts, a public and a private subset, each made up of $100$ acoustic scene recordings sampled at $44100\,\mathrm{Hz}$ and $30$ seconds in duration. The dataset is evenly divided into $10$ acoustic scene classes: \emph{bus}, \emph{busy street}, \emph{office}, \emph{open air market}, \emph{park}, \emph{quiet street}, \emph{restaurant}, \emph{supermarket}, \emph{tube}, and \emph{tube station}.
The recordings were made by three different recordists at a wide variety of locations in the Greater London area over a period of several months.
No systematic variations in the recordings covaried with scene
type: all recordings were made under moderate weather conditions, at varying times of day and week, and each recordist recorded each scene type. As a result, the dataset enjoys significant intra-class diversity while remaining of manageable size, making it suitable for evaluation of algorithmic design choices~\cite{lagrange:hal-01082501}.
